\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-19 NAR_DRAFT.tex
aml citation

Griffith et al.\ sequenced the whole genome of an acute myeloid leukemia (AML) primary tumor to a depth of $>$360X and used targeted sequencing to validate nearly 200,000 mutations~\cite{Griffith2015}.
We estimated a per-base mutation rate for this tumor of $4\cdot10^{-8}$, which would be considered normal in AML. \rngcomment{Really need a citation for this!}\bkmcomment{I have one, find it.}
For both MuTect and \batcave, the precision-recall curve is almost perfect for the validated variants (.995 \& .996 area under the curve) (Fig.~\ref{NAR-wes_fig}E and Table~\ref{table:01}).

>>>>

Griffith et al.\ sequenced the whole genome of an acute myeloid leukemia (AML) primary tumor to a depth of $>$360X and used targeted sequencing to validate nearly 200,000 mutations~\cite{Griffith2015}.
We estimated a per-base mutation rate for this tumor of $4\cdot10^{-8}$, which is inline with previous estimates of AML mutation rates \cite{Griffith2015,Williams2018}.
For both MuTect and \batcave, the precision-recall curve is almost perfect for the validated variants (.995 \& .996 area under the curve) (Fig.~\ref{NAR-wes_fig}E and Table~\ref{table:01}).
